Descriptive Complexity for Counting Complexity Classes

### 2018-12-09 LMCS/todo-list.tex
all direct replacements by reviewer 1

\item p.12: ``To formalize this set of optimization problems'': class instead of set

@@

\item p.18: ``Also, suppose that it is in $\L$-PNF'': $\L$ should be $\LL$ , PNF should be SNF
\item p.19, end of proof of Prop. 5.5: ``which violates the inequality'' $\to$ ``which violates the inequality

@@

\item p.20: ``we will show a formula in the grammar'' $\to$ ``... in the logic''

@@

\item p.22: ``and leaving each $R_{\psi}^{\A}$ empty'' $\to$ $R_{\psi}^{\A'}$

@@

\item p.22: ``Let $\alpha$ = ... where $\varphi$ is an FO-formula'' $\to$ ``... where $\varphi$ is an $\Sigma_1$[FO]-formula''

@@

\item p.24, formula 5.6: subscript of large conjunction: $\varphi_i^{+}(\bar{X},\bar{v})$ $\to$ $\varphi_i^{+}(\bar{X},\bar{y})$
\item p.25: ``We construct a function $\lambda$ that receives a quantitative formula $\beta$ ...'' $\to$ ``... that receives

@@

\martin{Punto posiblemente largo}
\item p.31, definition of $\leq$ on $\F$: ``$f(i) \leq g(i)$ for every $i \in \{1,\ldots,\ell\}$'': Inputs for $f$ and $g$ should be

@@

	\item p.3, first paragraph of 2.1: ``omit the word finite or ordered'' $\to$ ``omit the words finite and

@@

	\item p.5, next sentence: ``this will allow us later'' $\to$ ``this will later allow us''
	\item p.6, second to last sentence: ``similarity of $\alpha_3$ with'': ``similarity to'' is much more common

@@

	\item p.7, next sentence: ''in this direction'' $\to$ ``in this regard''
	\item p.7, last sentence before 3.1: ''connection of QSO with'' $\to$ ``connection of QSO to''
	\item p.7, middle: ``Another difference of WL with our approach'' $\to$ ``Another difference between

@@

	\item p.9, first paragraph: ``the constant function $s$ can be trivially simulated'' $\to$ ``any constant

@@

	\item p.9, proof of Prop. 4.3: ``To prove the condition (2)'' $\to$ ``To prove condition (2)''

@@

	\item p.12, after Corollary 4.8: ``shows how robust and versatile is QSO'' $\to$ ``shows how robust and

@@

	\item p.12, ``given CNF propositional formula, that can be made true'': no comma

@@

	\item p.12: ``we extend as follows QSO'' $\to$ ``we extend QSO by max and min quantifiers as follows''
	\item p.12: ``MinQSO is defined analogously changing max with min'' $\to$ ``replacing max by min''
	\item p.12: ``the same holds with MinQSO(FO)'' $\to$ ``the same holds for ...''
	\item p.13: ``in contrast with'' $\to$ ``in contrast to''
	\item p.13: ``follow the same approach but considering'' $\to$ ``but consider''
	\item p.13: ``in the search of efficient approximation algorithms'' $\to$ ``in the search for''
	\item p.14: ``the search of robust classes'' $\to$ ''the search for robust classes''

@@

	\item p.14: ``As in the cases of P and NP that are closed'' $\to$ ``Analogously to the cases of P and

@@

	\item p.16: ``such that for both, $A\mod\varphi(\bar{B}_i,\bar{b}_i,\bar{a}_i)$'' $\to$ ''such that for $i \in \{1,2\}$: ... ''
	\item p.16: ``Similarly to Theorem 5.1, we show ..'' $\to$ ``Similarly as in the proof of Theorem 5.1, we

@@

	\item p.19: ``Let ... be this formula, where $\varphi$ is in first-order and quantifier-free'' $\to$ ``... where $\varphi$ is

@@

	\item p.20: ``we focus only in proving'' $\to$ ``we focus only on proving''
	\item p.20: ``We prove this for a more general case for $\eqso(\LL)$ where $\LL$ is a fragment of FO.''

@@

	\item p.20: ``we will show a formula'' $\to$ ``give'' or ``construct'' instead of ``show''

@@

	\item p.21, next sentence: ``for a possible extension'' $\to$ ``as a possible extension''

@@

	\item p.21: ``a parsimonious reduction from a function'' $\to$ ``a parsimonious reduction from any

@@

	\item p.21: ``we define a function that converts a formula $\alpha$ in...'' $\to$ ``that converts a given formula

@@

	\item p.22: ``we iterate for every tuple'' $\to$ ``we iterate over all tuples''
	\item p.22: ``Then we will show how to define a formula $\varphi'$

@@

	\item p.22: ''no variable from $\bar{x}$ are mentioned'' $\to$ ``... is mentioned''

@@

	\item p.24: ``Then, the conclusion of the implication...'' $\to$ ``The conclusion of the implication...''
	\item p.25: ``For the sake of simplification...'' $\to$ ``For the sake of simplicity...''
	\item p.26: ``In the previous section, we show ...'' $\to$ ``In the previous section we showed ...''
	\item p.27: ``we postpone the proof the previous proposition after ...'' $\to$ ``we postpone the proof of

@@

	\item p.30: ``consist in computing $g_{\alpha}(\enc(\A))$ for each input ...'' $\to$ ``... on input ...''
	\item p.30, same sentence: ``and then simulate'' $\to$ ``and then simulating''
	\item p.33: ``In contrast with LFP'' $\to$ ``In contrast to LFP''
	\item p.33: ``These operations are represented by the set $\{0,1,\emptyset\}$, respectively.'' $\to$ ``... by 0, 1 and

@@

	\item p.34: ``Notice that the values of each function $f$ in $\alpha$'' $\to$ ``Notice that the values of each

@@

	\item p.34: ``that is why we talk about ...'' $\to$ ``which is why we talk about''
	\item p.34: ``Besides, notice that notation ...'' $\to$ ``Besides, notice that the notation ...''

@@

	\item p.36: ``Given a relation signature $\R$'' $\to$ ``... relational signature ...''
	\item p.37: ``As it was mentioned before'' $\to$ ``As mentioned before''
	\item p.37: ``Next we construct a logarithmic-space ....'' $\to$ ``We construct a logarithmic-space ...''

@@

	\item p4, beginning of 2.2: ``some of \underline{the} are recalled here''
	\item p6, example 3.2, first paragraph: ``otherwise $M(i.j)$'', dot used instead of comma
	\item throughout the paper: a instead of an (espacially: a FO formula/assignment, a SO formula/assignment).

@@

	\item p.9, middle: ``A second attempt could be based then'' $\to$ ``A second attempt could then be

@@

	\item p.11, 4.1: ``output of a function \underline{in} not a natural number''
	\item p.12: ``we have to dinstinguished''
	\item p.14, beginning of 5.1: ``subclases''
	\item p.21: ``it does not mentioned'' $\to$ ``it does not mention''
	\item p.22: ``Without lost of generality'' $\to$ ``Without loss of generality''
	\item p.24: ``The previous claim and proof motivates the following definitions.'' $\to$ ``The previous

@@

	\item p.30: ``this notion can be used to captures FP'' $\to$ ``... to capture FP''
	\item p.31: ``we simply generalized these conditions'' $\to$ ``we simply generalize these conditions''
	\item p.32: ``which is used to defined'' $\to$ ``which is used to define''
	\item p.33: ``since $\beta$ is constructed from monotones operations'' $\to$ ``... monotone ...''
	\item p.35: ``Formulas $\alpha_h$ is defined ...'' $\to$ ``Formula $\alpha_h$ is defined ...''

@@

	\item p.37: ``we simulate $M_\beta$ with input $v[1/n]$'' $\to$ ``... with input $v[1/x]$''

>>>>

\item[$\checkmark$] p.12: ``To formalize this set of optimization problems'': class instead of set

@@

\item[$\checkmark$] p.18: ``Also, suppose that it is in $\L$-PNF'': $\L$ should be $\LL$ , PNF should be SNF
\item[$\checkmark$] p.19, end of proof of Prop. 5.5: ``which violates the inequality'' $\to$ ``which violates the inequality

@@

\item[$\checkmark$] p.20: ``we will show a formula in the grammar'' $\to$ ``... in the logic''

@@

\item[$\checkmark$] p.22: ``and leaving each $R_{\psi}^{\A}$ empty'' $\to$ $R_{\psi}^{\A'}$

@@

\item[$\checkmark$] p.22: ``Let $\alpha$ = ... where $\varphi$ is an FO-formula'' $\to$ ``... where $\varphi$ is an $\Sigma_1$[FO]-formula''

@@

\item[$\checkmark$] p.24, formula 5.6: subscript of large conjunction: $\varphi_i^{+}(\bar{X},\bar{v})$ $\to$ $\varphi_i^{+}(\bar{X},\bar{y})$
\item[$\checkmark$] p.25: ``We construct a function $\lambda$ that receives a quantitative formula $\beta$ ...'' $\to$ ``... that receives

@@

\item[$\checkmark$] p.31, definition of $\leq$ on $\F$: ``$f(i) \leq g(i)$ for every $i \in \{1,\ldots,\ell\}$'': Inputs for $f$ and $g$ should be

@@

	\item[$\checkmark$] p.3, first paragraph of 2.1: ``omit the word finite or ordered'' $\to$ ``omit the words finite and

@@

	\item[$\checkmark$] p.5, next sentence: ``this will allow us later'' $\to$ ``this will later allow us''
	\item[$\checkmark$] p.6, second to last sentence: ``similarity of $\alpha_3$ with'': ``similarity to'' is much more common

@@

	\item[$\checkmark$] p.7, next sentence: ''in this direction'' $\to$ ``in this regard''
	\item[$\checkmark$] p.7, last sentence before 3.1: ''connection of QSO with'' $\to$ ``connection of QSO to''
	\item[$\checkmark$] p.7, middle: ``Another difference of WL with our approach'' $\to$ ``Another difference between

@@

	\item[$\checkmark$] p.9, first paragraph: ``the constant function $s$ can be trivially simulated'' $\to$ ``any constant

@@

	\item[$\checkmark$] p.9, proof of Prop. 4.3: ``To prove the condition (2)'' $\to$ ``To prove condition (2)''

@@

	\item[$\checkmark$] p.12, after Corollary 4.8: ``shows how robust and versatile is QSO'' $\to$ ``shows how robust and

@@

	\item[$\checkmark$] p.12, ``given CNF propositional formula, that can be made true'': no comma

@@

	\item[$\checkmark$] p.12: ``we extend as follows QSO'' $\to$ ``we extend QSO by max and min quantifiers as follows''
	\item[$\checkmark$] p.12: ``MinQSO is defined analogously changing max with min'' $\to$ ``replacing max by min''
	\item[$\checkmark$] p.12: ``the same holds with MinQSO(FO)'' $\to$ ``the same holds for ...''
	\item[$\checkmark$] p.13: ``in contrast with'' $\to$ ``in contrast to''
	\item[$\checkmark$] p.13: ``follow the same approach but considering'' $\to$ ``but consider''
	\item[$\checkmark$] p.13: ``in the search of efficient approximation algorithms'' $\to$ ``in the search for''
	\item[$\checkmark$] p.14: ``the search of robust classes'' $\to$ ''the search for robust classes''

@@

	\item[$\checkmark$] p.14: ``As in the cases of P and NP that are closed'' $\to$ ``Analogously to the cases of P and

@@

	\item[$\checkmark$] p.16: ``such that for both, $A\mod\varphi(\bar{B}_i,\bar{b}_i,\bar{a}_i)$'' $\to$ ''such that for $i \in \{1,2\}$: ... ''
	\item[$\checkmark$] p.16: ``Similarly to Theorem 5.1, we show ..'' $\to$ ``Similarly as in the proof of Theorem 5.1, we

@@

	\item[$\checkmark$] p.19: ``Let ... be this formula, where $\varphi$ is in first-order and quantifier-free'' $\to$ ``... where $\varphi$ is

@@

	\item[$\checkmark$] p.20: ``we focus only in proving'' $\to$ ``we focus only on proving''
	\item[$\checkmark$] p.20: ``We prove this for a more general case for $\eqso(\LL)$ where $\LL$ is a fragment of FO.''

@@

	\item[$\checkmark$] p.20: ``we will show a formula'' $\to$ ``give'' or ``construct'' instead of ``show''

@@

	\item[$\checkmark$] p.21, next sentence: ``for a possible extension'' $\to$ ``as a possible extension''

@@

	\item[$\checkmark$] p.21: ``a parsimonious reduction from a function'' $\to$ ``a parsimonious reduction from any

@@

	\item[$\checkmark$] p.21: ``we define a function that converts a formula $\alpha$ in...'' $\to$ ``that converts a given formula

@@

	\item[$\checkmark$] p.22: ``we iterate for every tuple'' $\to$ ``we iterate over all tuples''
	\item[$\checkmark$] p.22: ``Then we will show how to define a formula $\varphi'$

@@

	\item[$\checkmark$] p.22: ''no variable from $\bar{x}$ are mentioned'' $\to$ ``... is mentioned''

@@

	\item[$\checkmark$] p.24: ``Then, the conclusion of the implication...'' $\to$ ``The conclusion of the implication...''
	\item[$\checkmark$] p.25: ``For the sake of simplification...'' $\to$ ``For the sake of simplicity...''
	\item[$\checkmark$] p.26: ``In the previous section, we show ...'' $\to$ ``In the previous section we showed ...''
	\item[$\checkmark$] p.27: ``we postpone the proof the previous proposition after ...'' $\to$ ``we postpone the proof of

@@

	\item[$\checkmark$] p.30: ``consist in computing $g_{\alpha}(\enc(\A))$ for each input ...'' $\to$ ``... on input ...''
	\item[$\checkmark$] p.30, same sentence: ``and then simulate'' $\to$ ``and then simulating''
	\item[$\checkmark$] p.33: ``In contrast with LFP'' $\to$ ``In contrast to LFP''
	\item[$\checkmark$] p.33: ``These operations are represented by the set $\{0,1,\emptyset\}$, respectively.'' $\to$ ``... by 0, 1 and

@@

	\item[$\checkmark$] p.34: ``Notice that the values of each function $f$ in $\alpha$'' $\to$ ``Notice that the values of each

@@

	\item[$\checkmark$] p.34: ``that is why we talk about ...'' $\to$ ``which is why we talk about''
	\item[$\checkmark$] p.34: ``Besides, notice that notation ...'' $\to$ ``Besides, notice that the notation ...''

@@

	\item[$\checkmark$] p.36: ``Given a relation signature $\R$'' $\to$ ``... relational signature ...''
	\item[$\checkmark$] p.37: ``As it was mentioned before'' $\to$ ``As mentioned before''
	\item[$\checkmark$] p.37: ``Next we construct a logarithmic-space ....'' $\to$ ``We construct a logarithmic-space ...''

@@

	\item[$\checkmark$] p4, beginning of 2.2: ``some of \underline{the} are recalled here''
	\item[$\checkmark$] p6, example 3.2, first paragraph: ``otherwise $M(i.j)$'', dot used instead of comma
	\item[$\checkmark$] throughout the paper: a instead of an (espacially: a FO formula/assignment, a SO formula/assignment).

@@

	\item[$\checkmark$] p.9, middle: ``A second attempt could be based then'' $\to$ ``A second attempt could then be

@@

	\item[$\checkmark$] p.11, 4.1: ``output of a function \underline{in} not a natural number''
	\item[$\checkmark$] p.12: ``we have to dinstinguished''
	\item[$\checkmark$] p.14, beginning of 5.1: ``subclases''
	\item[$\checkmark$] p.21: ``it does not mentioned'' $\to$ ``it does not mention''
	\item[$\checkmark$] p.22: ``Without lost of generality'' $\to$ ``Without loss of generality''
	\item[$\checkmark$] p.24: ``The previous claim and proof motivates the following definitions.'' $\to$ ``The previous

@@

	\item[$\checkmark$] p.30: ``this notion can be used to captures FP'' $\to$ ``... to capture FP''
	\item[$\checkmark$] p.31: ``we simply generalized these conditions'' $\to$ ``we simply generalize these conditions''
	\item[$\checkmark$] p.32: ``which is used to defined'' $\to$ ``which is used to define''
	\item[$\checkmark$] p.33: ``since $\beta$ is constructed from monotones operations'' $\to$ ``... monotone ...''
	\item[$\checkmark$] p.35: ``Formulas $\alpha_h$ is defined ...'' $\to$ ``Formula $\alpha_h$ is defined ...''

@@

	\item[$\checkmark$] p.37: ``we simulate $M_\beta$ with input $v[1/n]$'' $\to$ ``... with input $v[1/x]$''
